Online {\IterComp}

### 2017-09-15 motivation.tex
updates figures

    \begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figs/motivation-metric.pdf}
        \caption{
            Relationship between IPC and execution time vs optimization speedup for 500 different binaries of \texttt{susan\_c}.
            Each point represents averages over a subset of all inputs.
            The IPC shows a correlation coefficient of $-0.14$.
        }
        \label{fig:motivation-metric}
    \end{figure}

>>>>

    \begin{figure}[t]
        \centering
        %\begin{tabular}{cc}
        %\includegraphics[width=0.25\textwidth]{figs/motivation-metric-ipc.pdf} &
        %\includegraphics[width=0.25\textwidth]{figs/motivation-metric-runtime.pdf}
        %\end{tabular}
        \includegraphics[width=0.5\textwidth]{figs/motivation-metric.pdf}
        \caption{
            Relationship between IPC and execution time \textit{vs} speedup over the unoptimized program
            for 500 different binaries of \texttt{susan\_c}.
            Each point represents the average over a subset of all inputs.
            The IPC and execution time show correlation coefficients of $-0.14$ and $-0.16$, respectively.
        }
        \label{fig:motivation-metric}
    \end{figure}

### 2017-09-15 work.tex
updates figures

    \begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figs/motivation-work-efficiency.pdf}
        \caption{Relationship between work efficiency vs speedup for 500 different binaries of \texttt{susan\_c}.
                Each point represents averages over a subset of all inputs.
                Correlation coefficient of $0.93$.}
        \label{fig:motivation-work-efficiency}
    \end{figure}

>>>>

    \begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figs/motivation-work-efficiency.pdf}
        \caption{Relationship between work efficiency \textit{vs} speedup for 500 different binaries of \texttt{susan\_c}.
                Each point represents the average over a subset of all inputs.
                The correlation coefficient is $0.93$.}
        \label{fig:motivation-work-efficiency}
    \end{figure}
